%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional CV Template - V5
%
% Revisions based on user feedback:
% 1. Increased spacing in Employment History (after title and date).
% 2. Increased spacing after Skill Category headers.
% 3. Verified individual skills are regular weight while categories are bold.
%
% Created by Gemini
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, a4paper]{article}

% --- PACKAGES ---
\usepackage[a4paper, margin=0.5in, nohead, nofoot]{geometry} % Page dimensions
\usepackage{paracol}          % For two-column layout that can break across pages
\usepackage[T1]{fontenc}      % Font encoding
\usepackage[default,light]{lato} % USE LATO LIGHT FONT for a lighter, modern feel
\usepackage[svgnames]{xcolor} % For custom colors
\usepackage{hyperref}         % For clickable links
\usepackage{enumitem}         % For customizing lists
\usepackage{setspace}         % To adjust line spacing

% --- GLOBAL SPACING ---
% Increased line spacing for better readability within paragraphs
\setstretch{1.1}

% --- COLOR & HYPERLINK DEFINITIONS ---
\definecolor{sidebarbg}{HTML}{2C3E50} % Dark slate blue for the sidebar
\definecolor{linkcolor}{HTML}{5DADE2} % A lighter blue for links
\definecolor{dategray}{gray}{0.55}   % Dark gray for de-emphasized dates

\hypersetup{
    pdftitle={Siddharth Tandon CV},
    pdfauthor={Siddharth Tandon},
    colorlinks=true,
    urlcolor=linkcolor,
    linkcolor=linkcolor,
}

% --- PAGE & PARAGRAPH STYLING ---
\pagestyle{empty}      % No page numbers, headers, or footers
\setlength{\parindent}{0pt} % No paragraph indentation
\setlength{\columnsep}{1.5em} % Space between the two columns

% --- CUSTOM COMMANDS FOR SECTIONS ---

% Section style for the main (left) column
\newcommand{\cvsection}[1]{%
  \vspace{1.2\baselineskip}%
  {\large\bfseries\sffamily\MakeUppercase{#1}}\par\vspace{0.4ex}%
  {\color{black!70}\hrule height 0.8pt}\par
  \vspace{0.8\baselineskip}%
}

% Section style for the sidebar (right) column
\newcommand{\sidebarsection}[1]{%
  \vspace{1.2\baselineskip}%
  {\color{white}\bfseries\sffamily\MakeUppercase{#1}}\par%
  \vspace{0.6ex}%
  {\color{white!60}\hrule height 0.6pt}\par% % UPDATED: Added a decorative line
  \vspace{0.5\baselineskip}%
}

% Sub-heading style for skills in the sidebar
\newcommand{\skillcat}[1]{%
    \vspace{0.8\baselineskip}%
    {\bfseries\sffamily #1}\par\vspace{1.0ex}% % UPDATED: Increased vertical space after category
}

% --- LIST STYLING (for bullet points) ---
\setlist[itemize]{
  leftmargin=1.5em,  % Indentation of bullets
  label=\textbullet,   % Bullet style
  topsep=0.3ex,      % Space above list
  itemsep=1.2ex,     % Increased space between items for readability
  parsep=0ex
}

\begin{document}

% --- LAYOUT SETUP: 65% for main content, 35% for sidebar ---
\setcolumnwidth{0.65\textwidth, 0.35\textwidth}
\backgroundcolor{c[1]}{sidebarbg} % Set background color for the second column

\begin{paracol}{2}

%================================================%
% --- LEFT COLUMN (MAIN CONTENT) ---
%================================================%

% --- HEADER ---
{\fontsize{24pt}{26pt}\selectfont\bfseries Siddharth Tandon}\par
\vspace{0.5ex}
{\fontsize{12pt}{14pt}\selectfont AI Architect/ Applied Scientist/  Data Scientist}\par

% --- PROFILE SECTION ---
\cvsection{Summary}
Results-driven AI/ML Specialist with over 14 years of experience in developing and deploying machine learning models. Expertise in data analysis, algorithm development, statistical models and project management, with a commitment to leverage technology for impactful solutions. Proven track record of solving complex challenges and driving innovation through advanced analytical skills and strategic problem-solving. 

% --- EMPLOYMENT SECTION ---
\cvsection{Employment}
{\bfseries Strategic Cloud Engineer, Google}\par
\vspace{0.5ex} % UPDATED: Added space between title and date
{\color{dategray}\itshape\MakeUppercase{Jun 2022 – Present}}
\vspace{1.0ex} % UPDATED: Added space after date before bullet points
\begin{itemize}
    \item Led the Nl2SQL implementation for a customer using ADK framework.
    \item Led the program for entire team to enhance fine tuning expertise (using LoRA, QLoRA, Vertex AI) within team, and guided more than 10+ pre-sales for customers.
    \item Presented a poster in Google Research Conference 2023 for "Explicit content detection using large vision models with contrastive objective". This also got published as one of the case \href{https://cloud.google.com/customers/nexon/?hl=ko}{studies} in public domain.
    \item Distributed training/ inferencing of large language models on TPU/ GPUs using \href{https://github.com/tensorflow/lingvo}{lingvo framework}.
    \item Architected AI solutions for strategic customers.
    \item Lead and implemented multiple Gen AI solutions across various use cases like summarization, RAG, etc.
    \item Build and deployed multiple agentic systems leveraging frameworks like Langchain, Langgraph.
    \item Deep expertise on Data Valuation using SHAP methodology.
\end{itemize}
\vspace{1.2\baselineskip} % Add generous vertical space between jobs

{\bfseries AI \& ML Solution Architect, Microsoft}\par
\vspace{0.5ex} % UPDATED: Added space between title and date
{\color{dategray}\itshape\MakeUppercase{Apr 2020 – Jun 2022}}
\vspace{1.0ex} % UPDATED: Added space after date before bullet points
\begin{itemize}
    \item Implemented yield forecasting to assist in supply chain by leveraging vegetation indices and land images from satellite data.
    \item Implement ML models/ MLOPS to help customers in their AI journey.
    \item Implemented deep learning models to detect defects in parts (using transfer learning), brain segmentation using FCNNs.
    \item Implemented predictive/ forecasting models for manufacturing customers.
    \item Leveraged cognitive APIs for search, text translation for various use cases.
    \item Certified Microsoft Enterprise Data Science practitioner/ proctor.
    \item Drive, define, and implement AI initiatives for customers on Azure.
    \item Build end to end solution architecture for large scale technology projects.
    \item Implement/ assist customers with big data solutions to digitize their data estate.
    \item Manage client stakeholders, and their expectations, with regular cadence of weekly meetings and status updates.
    \item Define business case for technological investments to be made for future needs and to remain competitive.
\end{itemize}
\vspace{1.2\baselineskip} % Add generous vertical space between jobs

{\bfseries Consultant, Microsoft}\par
\vspace{0.5ex} % UPDATED: Added space between title and date
{\color{dategray}\itshape\MakeUppercase{Nov 2014 – Mar 2020}}
\vspace{1.0ex} % UPDATED: Added space after date before bullet points
\begin{itemize}
    \item Architected and implemented big data solutions using Delta, Lambda and Kappa architecture leveraging Spark framework and Azure technologies.
    \item Assisted data scientists to build ML models like detect fraudulent transactions, lead generation for customers, etc.
    \item Lead multiple Data \& AI projects and moved them to production successfully.
    \item Delivered sessions and mentored peers on big data technology landscape.
    \item Assisted in the recruitment process for the team.
\end{itemize}
\vspace{1.2\baselineskip} % Add generous vertical space between jobs

{\bfseries Sr. Software Engg., MAQ Software}\par
\vspace{0.5ex} % UPDATED: Added space between title and date
{\color{dategray}\itshape\MakeUppercase{Jul 2011 – Oct 2014}}
\vspace{1.0ex} % UPDATED: Added space after date before bullet points
\begin{itemize}
    \item Implemented data warehouses and OLAP cubes. 
    \item Collaborate with stakeholders/ clients to gather and analyze business requirements.
    \item Actively involved in effort estimation, deployment plans, test plans and peer code reviews.
    \item Break the requirements into tasks and allocate them within the team.
    \item Responsible for delivering the project within a specified time frame.
    \item Analyze changes and incorporate them in sprint as per the bandwidth and complexity.
\end{itemize}

% --- EDUCATION SECTION ---
\cvsection{Education}
{\bfseries IIT, Hyderabad} \hfill MTech \par
\textit{2020 – 2023}
\vspace{2ex}

{\bfseries AKGEC} \hfill BTech \par
\textit{2007 – 2011}

% --- PAPERS SECTION ---
\cvsection{Papers}
{\bfseries \href{https://cmsworkshops.com/ICASSP2024/view_paper.php?PaperNum=4738}{FW-SHAPLEY: REAL-TIME ESTIMATION OF WEIGHTED SHAPLEY VALUES} (ICASSP 2024)}\par
\begin{itemize}
    \item Accepted in ICASSP 2024 under Explainable and Interpretable Machine Learning area.
    \item Introduced an amortized framework for weighted Shapley value computation for feature attribution and data valuation setting in real-time via a learned estimator without actual target variable.
\end{itemize}
\vspace{1.5\baselineskip}
{\bfseries Explicit content detection (Google Research 2023)}\par
\begin{itemize}
    \item Detect explicit content using large vision models with contrastive objective.
\end{itemize}


%================================================%
% --- RIGHT COLUMN (SIDEBAR) ---
%================================================%
\switchcolumn

\color{white} % Set text color to white for the entire sidebar
\leftskip1em  % Add a small left margin/padding to the sidebar content
\rightskip1em % Add a small right margin/padding
\vspace*{2.5\baselineskip} % Added vertical space at the top of the sidebar

\sidebarsection{Details}
(+91) 905 269 8726\par
\vspace{0.5ex}
\href{mailto:siddharth.tandon1@gmail.com}{siddharth.tandon1@gmail.com}
    
\sidebarsection{Links}
\href{https://scholar.google.com/citations?view_op=list_works&hl=en&authuser=1&user=REyR8UEAAAAJ}{Google Scholar}\par
\vspace{0.5ex}
\href{https://github.com/sidtandon2014}{GitHub}\par
\vspace{0.5ex}
\href{http://www.linkedin.com/in/siddharthtandon1}{LinkedIn}\par

\sidebarsection{Skills}
\skillcat{Generative AI}
Agentic AI\par\vspace{0.4ex}
RAG\par\vspace{0.4ex}
Text Generation\par\vspace{0.4ex}
Image Generation\par\vspace{0.4ex}

\skillcat{Machine Learning}
Probabilistic Models\par\vspace{0.4ex}
Non-Probabilistic Models\par\vspace{0.4ex}
Linear and Logistic Regression\par\vspace{0.4ex}
Trees and Ensembling\par\vspace{0.4ex}
SVM\par\vspace{0.4ex}
Neural Networks\par\vspace{0.4ex}
Clustering\par\vspace{0.4ex}
Regularization\par\vspace{0.4ex}
Dimensionality Reduction\par\vspace{0.4ex}
Linear Algebra\par

\skillcat{Deep Learning}
CNN\par\vspace{0.4ex}
NLP\par\vspace{0.4ex}
Image Classification\par\vspace{0.4ex}
Image Segmentation\par\vspace{0.4ex}
Large Language Models\par\vspace{0.4ex}
Generative AI\par\vspace{0.4ex}
Inference Optimization\par

\skillcat{Frameworks/ Languages}
Python\par\vspace{0.4ex}
SQL\par\vspace{0.4ex}
Pytorch\par\vspace{0.4ex}
ADK\par\vspace{0.4ex}
Langchain\par\vspace{0.4ex}
Langgraph\par\vspace{0.4ex}
    

\skillcat{Reinforcement Learning}
Dynamic Programming\par\vspace{0.4ex}
Monte carlo methods\par\vspace{0.4ex}
TD methods\par\vspace{0.4ex}
Deep Q Networks\par\vspace{0.4ex}
RLHF/ RLAIF\par\vspace{0.4ex}
Policy gradient (GRPO, DPO)\par

\skillcat{Use cases}
Predictive Modelling\par\vspace{0.4ex}
Forecasting\par\vspace{0.4ex}
Regression and classification\par\vspace{0.4ex}
Defect Detection\par\vspace{0.4ex}
Advanced Search\par\vspace{0.4ex}

\sidebarsection{Certificates}
Google Cloud Professional Machine Learning Engineer\par\vspace{0.4ex}
Microsoft Certified: Enterprise Data Science Practitioner\par\vspace{0.4ex}
Microsoft Certified: Azure Data Scientist Associate\par\vspace{0.4ex}
Microsoft Certified: Azure Data Engineer Associate\par\vspace{0.4ex}
Microsoft Certified: Azure AI Engineer Associate\par\vspace{0.4ex}


\end{paracol}
\end{document}